Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Edited abstract
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1622 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: 
supporting for the syntax-augmented machine translation (SAMT) grammar,
support for external modules to posit translations for spans in the input sentence that constrain decoding,  
lattice parsing for dealing with input uncertainty,
semiring parsing for unified dynamic programming, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees and hypergraphs, 
and a unified pipeline for MT experiments.
\end{abstract}

\listoftodos

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

@@

\section{Specifying Constraints on the Rules}
\todo{anni}

>>>>

\maketitle
\begin{abstract}
We describe the progress we have made in the past year on \textbf{Joshua} \cite{joshua-wmt09}, 
an open source toolkit for parsing based machine translation.
The new functionality includes: 
support for translation grammars with a rich set of syntactic nonterminals,
the ability for external modules to posit constraints on spans in the input sentence should be translated,  
lattice parsing for dealing with input uncertainty,
a semiring framework that provides a unified way of doing various dynamic programming calculations, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees, 
and a cleaner pipeline for MT experiments.
\end{abstract}

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit for parsing-based machine translation (written in Java). 
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

@@

\section{Specifying Constraints on Rules}
\todo{anni}
